Bx to Rev (tentative) \thanks{Supported by organization x.}

### 2019-08-23 paper/main.tex
Update main.tex

This section describes the experiments involving $minBiGUl$, $pg$, $cpg$, $kpg$ and $xpg$. The evaluation time, the memory allocation and the number of function calls are considered in each test.

@@

The above definition contains an adaptive branch and it only occurs when the length of the source and the view are different. If we restrict them as two lists whose same lengths, the case analysis will only evaluate the normal branch. For test case $breverse$ in table \ref{tab:test-cases}, we choose both $s_0$ and $v_0$ as lists from 1 to $n$. Then, the results $s_r$ and $v_r$ are the list from $n$ to 1. Explicitly, $\putbx{bReverse}{[1..n]}{[1..n]} = [n..1]$ and $\getbx{bReverse}{[1..n]} = [n..1]$. In $bReverse$, the number of composition equals to the length of the source and the view.

\subsection{Results and discussions}
We conducted experiments on 5 test cases while changing the number of composition from 10 to 100000.

@@

                xlabel = {number of composition},

@@

                legend style = {font=\scriptsize},
                legend pos = north west

@@

                xlabel = {number of composition},

@@

                legend style = {font=\scriptsize},
                legend pos = north west

@@

                legend style = {font=\scriptsize},
                legend pos = north east

@@

                legend style = {font=\scriptsize},
                legend pos = north east

@@

                legend style = {font=\scriptsize},
                legend pos = north east

@@

@@

                legend style = {font=\scriptsize},
                legend pos = north east

@@

>>>>

This section describes the experiments involving $minBiGUl$, $pg$, $cpg$, $kpg$ and $xpg$. The number of function calls, the evaluation time and the memory allocation are considered in each test.

@@

The above definition contains an adaptive branch and it only occurs when the lengths of the source and the view are different. If we restrict them as two lists whose same lengths, the case analysis will only evaluate the normal branch. For test case $breverse$ in table \ref{tab:test-cases}, we choose both $s_0$ and $v_0$ as lists from 1 to $n$. Then, the results $s_r$ and $v_r$ are the list from $n$ to 1. Explicitly, $\putbx{bReverse}{[1..n]}{[1..n]} = [n..1]$ and $\getbx{bReverse}{[1..n]} = [n..1]$. In $bReverse$, the number of compositions equals to the length of the source and the view.

\subsection{Results and discussions}

@@

                xlabel = {number of compositions},
                ylabel = {number of calls},
                legend style = {font=\scriptsize,at={(0.15,0.78)},anchor=west},
                \pgfplotstableread[col sep=comma]{csv/count-lassoc-comp-replace.csv}\data
                \addplot table[x=nComp,y=count_get]{\data};
                \addlegendentry{get};
                \addplot table[x=nComp,y=count_put]{\data};
                \addlegendentry{put};
                \addplot table[x=nComp,y=count_pg]{\data};
                \addplot table[x=nComp,y=count_xpg]{\data};
                \addlegendentry{cpg/kpg/xpg};
                xlabel = {number of compositions},
                legend style = {font=\scriptsize,at={(0.03,0.78)},anchor=west},
                \pgfplotstableread[col sep=comma]{csv/count-rassoc-comp-replace.csv}\data
                \addplot table[x=nComp,y=count_get]{\data};
                \addlegendentry{get};
                \addplot table[x=nComp,y=count_put]{\data};
                \addlegendentry{put};
                \addplot table[x=nComp,y=count_pg]{\data};
                \addplot table[x=nComp,y=count_xpg]{\data};
                \addlegendentry{cpg/kpg/xpg};
                xlabel = {number of compositions},
                ylabel = {number of calls},
                legend style = {font=\scriptsize,at={(0.15,0.78)},anchor=west},
                \pgfplotstableread[col sep=comma]{csv/count-lassoc-comp-phead.csv}\data
                \addplot table[x=nComp,y=count_get]{\data};
                \addlegendentry{get};
                \addplot table[x=nComp,y=count_put]{\data};
                \addlegendentry{put};
                \addplot table[x=nComp,y=count_pg]{\data};
                \addplot table[x=nComp,y=count_xpg]{\data};
                \addlegendentry{cpg/kpg/xpg};
                xlabel = {number of compositions},
                legend style = {font=\scriptsize,at={(0.03,0.78)},anchor=west},
                \pgfplotstableread[col sep=comma]{csv/count-rassoc-comp-phead.csv}\data
                \addplot table[x=nComp,y=count_get]{\data};
                \addlegendentry{get};
                \addplot table[x=nComp,y=count_put]{\data};
                \addlegendentry{put};
                \addplot table[x=nComp,y=count_pg]{\data};
                \addplot table[x=nComp,y=count_xpg]{\data};
                \addlegendentry{cpg/kpg/xpg};
                xlabel = {number of compositions},
                ylabel = {number of calls},
                legend style = {font=\scriptsize,at={(0.47,0.78)},anchor=west},
                \pgfplotstableread[col sep=comma]{csv/count-breverse.csv}\data
                \addplot table[x=nComp,y=count_get]{\data};
                \addlegendentry{get};
                \addplot table[x=nComp,y=count_put]{\data};
                \addlegendentry{put};
                \addplot table[x=nComp,y=count_pg]{\data};
                \addplot table[x=nComp,y=count_xpg]{\data};
                \addlegendentry{cpg/kpg/xpg};
    \caption{Number of calls}
    \label{fig:count-calls}
                xlabel = {number of compositions},

@@

                legend style = {font=\scriptsize,at={(0.2,0.75)},anchor=west},

@@

                xlabel = {number of compositions},

@@

                legend style = {font=\scriptsize,at={(0.03,0.75)},anchor=west},

@@

                legend style = {font=\scriptsize,at={(0.03,0.75)},anchor=west},

@@

                legend style = {font=\scriptsize,at={(1.03,0.75)},anchor=west},

@@

                legend style = {font=\scriptsize,at={(0.2,0.75)},anchor=west},

@@

                \addlegendentry{minbigul};x

@@

                legend style = {font=\scriptsize,at={(0.57,0.75)},anchor=west},

@@

\begin{table}[]
    \centering
    \caption{Comparison}
    \label{tab:comparison}
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{|l|l|l|l|}
            \hline
            \multicolumn{1}{|c|}{Name} & \multicolumn{1}{c|}{Properties} & \multicolumn{1}{c|}{Evaluation time order} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Memory allocation order\\ (stack\_overflow point / 100000)\end{tabular}} \\ \hline
            lassoc-comp-replace & l, NR & kpg $\sim$ xpg $<$ cpg $<$ minbigul $<$ pg & minbigul $<$ cpg $<$ kpg $\sim$ xpg (95299) $<$ pg (ND) \\ \hline
            rassoc-comp-replace & r, NR & minbigul $<$ pg $<$ xpg $<$ cpg $<$ kpg & minbigul $<$ pg $<$ xpg $<$ cpg (95299) $<$ kpg (80638) \\ \hline
            lassoc-comp-phead & l, NR & xpg $<$ kpg $<$ minbigul $<$ cpg $<$ pg & minbigul $<$ kpg $\sim$ xpg (80638) $<$ cpg (ND) $<$ pg (ND) \\ \hline
            rassoc-comp-phead & r, NR & minbigul $<$ pg $<$ xpg $<$ cpg $<$ kpg & minbigul $<$ pg $<$ xpg $<$ cpg (43680) $<$ kpg (61665) \\ \hline
            breverse & l, R & xpg $<$ kpg $<$ minbigul $<$ cpg $<$ pg & xpg (ND) $<$ kpg (ND) $<$ cpg (ND) $<$ minbigul (ND) $<$ pg (ND) \\ \hline
            \multicolumn{4}{r}{} \\
            \multicolumn{4}{r}{l/r: left/right associative} \\
            \multicolumn{4}{r}{NR/R: non-recursive/recursive} \\
            \multicolumn{4}{r}{ND: not determined} \\
            \multicolumn{4}{r}{best $< \ldots <$ worst} \\
        \end{tabular}%
    }
    \end{table}
